Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-16 manuscript/response_to_reviews.Rmd

[*issue #94*](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/94)

**We have gone through the manuscript / tables and figures and updated where it said "dAICc" to be $\Delta$AICc. **

Following the two previous comments, I suggest to leave in Table 5 just the best model (rather that a multimodel inference as is presented now) to discuss more clearly the covariates included. And I suggest discussing only the model with all years together. This would be more robust and avoid ramble differences between years that mostly look spurious and with a difficult physiological explanation. This would help to ensure a better use of the Resilience indices.

**In the spirit of this comment (simplifying presentation), we have created a new figure (*Fig. 4*) visualizing the results of the best model. We moved Table 5 to the Appendix (now Table S6, plus a parallel Table S7 for $Rt_{ARIMA}$).**

**We have also dramatically decreased the emphasis on differences across drought years, as follows:* **

**(1) Table 1 now shows just the results from the model with all drought years combined.**

**(2) The results and discussion now focus on the results from the three drought years combined.**

**(3) In order to make models more consistent across years and reduce spurious correlations, we now include the criteria that for a trait to be included as a candidate variable in the full model, the sign of coefficients must be consistent across all droughts (in addition to meeting the AIC criteria, as before). This resulted in only two candidate variables for the main model ($PLA_{dry}$ and $\pi_{tlp}$). (Removed was ring porosity, which had opposite effects in different droughts.)**

*We do plot the three droughts separately in figures **#,#**, as we do fee that this makes the story richer.*

@@

**We agree that this could be a concern, but do not believe it is applicable here, for two reasons. First, this would be more likely to introduce a bias if the trees cored dead were killed by drought. We are aware of studies showing differences in climate sensitivity of trees killed by drought versus those that survived. However,these trees were not killed by drought; there was no significant drought in the years in which dead trees were cored or in the 3 previous years. Second, quoting our previous publication using these cores (Helcoski et al. 2019): " Chronologies of trees cored live and dead were pooled following analyses showing similar climate sensitivity at least up to 2009 (that is excluding 7–8 yr before death) for all four species with ≥ 10 cores in each category (LITU, QURU, QUVE, FRAM; comparison plots available at https://github.c om/SCBI-ForestGEO/climate_sensitivity_cores/tree/master/ results/live_vs_dead).".**

**To clarify that this shouldn't be an issue, we have added the following sentence (methods section): "We note that drought was probably not a cause of mortality for these trees, as monthly May-Aug $PDSI$ did not drop below -1.75 in these years or the three years prior (2013-2017), and that trees cored dead displayed similar climate sensitivity to trees cored live [@helcoski_growing_2019]."**

L165-167: I think this needs to be explained more clearly. Why are type I errors unlikely and type II error possible? I also think there are real issue with the analysis of crown position. Presumably on average the crown illumination index of trees would have increased over the past 50 or so years (from suppressed to dominant) as trees grew and neighbouring trees died. So I’m not convinced you can include this in your models going back half a century. It’s just not sensible to assume that crown position would not have changed over such a long time period.

**We no longer attempt to use crown position to describe variation in drought resistance. Instead, we now use it to characterize *contemporary* differences in microenvironmental conditions faced by trees of different heights.**

### 2020-07-16 manuscript/response_to_reviews.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Response to reviews},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\title{Response to reviews}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\emph{italics - temporary comments for points that remain to be
addressed}

\textbf{bold - response}

\textasciitilde\textasciitilde\textasciitilde\textasciitilde{}

@@

Dear Editor:

\ldots{} Major changes included the following:

\begin{itemize}
\item
  At the request of 3 reviewers (R1,R3,R4), we tried an alternate metric
  of drought resistance (using an ARIMA model to project what growth
  would have been in drought year based on the trend over the past 10
  years). Results were similar, and we now present that as a secondary
  model (mostly in SI).
\item
  We slightly modified the method of determining which trait variables
  go into the full model. Specifically, we added the criteria of
  consistent direction across droughts, and as a result dropped xylem
  porosity. This also makes sense because the two diffuse porous species
  (Liriodendron tulipifera and Fagus grandifolia) are at opposite ends
  of the spectrum in terms of drought resistance. (Side note: this
  contradicts the current understanding that diffuse porous species in
  the temperate deciduous biome are more drought sensitive, but not the
  bigger global picture, as R2 points out.).
\item
  We moved former tables 4 and 5 to the SI.
\item
  We added two figures: one showing Rt differences across species, and
  one visualizing the model results (the latter is not yet right, as
  gg-plot is being difficult, but will eventually match the model
  results.)
\end{itemize}

@@

The result is an easier to read paper with more robust support.

\newpage

\hypertarget{referee-1}{%
\subsection{Referee: 1}\label{referee-1}}

@@

Comments to the Author

The study addresses the relationship between drought resistance (Rt)
calculated from radial growth, and different traits and
microenvironmental characteristics on 12 tree species from one forest in
the Eastern US. Both the dataset and the study are meaningful, and the
relationship found between Rt and height of biological importance.
However, I think there are a number of issues that need to be worked
out.

It is important to better discuss the proper use of Rt, particularly
when comparing single drought years, to assess tree resistance to
drought. This metric has been much used lately as one of the so-called
resilience indices (I wonder why other Rs indices where not included in
the manuscript). In the paper, the authors use Rt similarly to most
studies in the literature, which is fine. Yet, Rt (and particularly the
other resilience indices based on radial growth) does not only depend on
the individual response to drought events, but also on stand dynamics
around target trees. For this reason, if stands around trees are not
comparable or show changes after some disturbance (e.g.~the drought
events analysed) differently, this may bias comparisons of Resilience
indices (although it is true that Rt should be less influenced than the
other indices). The problem is that there is not such stand competition
data for old droughts. This does not invalidate the study but I think
the authors should discuss the issue, particularly for the analysis and
comparisons of single droughts. I would suggest including also other
Resilience indices, not only Rt, to enrich the discussion.

\href{https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/92}{\emph{issue
\#92}}

\textbf{To account for potential trends in individual tree growth prior
to the drought, which could be influenced by stand dynamics, we tried an
intervention time series analysis (ARIMA). Details on the comparison
between \(Rt\) and \(Rt_{ARIMA}\) are presented in the responses to
reviewer 4. In short, the ARIMA method yielded broadly similar results,
but tended to produce less reasonable estimates when the difference
between the two metrics was large, so we decided to retain \(Rt\) as the
focal metric. While this unquestionably leads to biased estimates for
some trees, we would not expect it to bias our analysis; rather, it is
one of the reasons that the amount of variation that can be explained by
analyses such as these is relatively low. We now include the following
content on ARIMA in the manuscript:}

(\emph{insert text})

\textbf{Regarding the resilience indices, we considered analyzing these
and decided it would be best to stick with just resistance for three
reasons: (1) Most importantly, we would expect resilience to be governed
by fundamentally different mechanisms than resistance. While it would be
interesting to examine resilience, this would be beyond the scope of the
current paper. (2)
\href{https://www.nature.com/articles/s41467-020-14300-5}{DeSoto et
al.~(2020, Nature)} used an extensive dataset of trees sampled after
severe droughts and compared the responses to previous, less-severe
droughts between trees that survived and trees that were killed by the
severe drought. In angiosperms, trees that died from a severe drought
had lower resistance to previous droughts, compared to trees that
survived the severe drought. In gymnosperms, trees that died during
severe droughts had lower recovery following previous droughts, compared
to trees that survived the severe drought. These findings would argue
that resistance is a more important variable for angiosperms. (3) As the
reviewer notes, resilience indices would probably tend to be more
sensitive to a tree's neighborhood and prior conditions. We now state
the logic for focusing on \(Rt\) in the methods section:}

\textbf{``We focus exclusively on drought resistance (\(Rt\) or
\(Rt_{ARIMA}\)), and not on the resilience metrics described in Lloret
\emph{et al.} (2011), because (1) we would expect resilience to be
controlled by a different set of mechanisms, and (2) the findings of
\emph{\href{https://www.nature.com/articles/s41467-020-14300-5}{DeSoto
et al.~(2020)}} suggest that \(Rt\) is a more important drought response
metric for angiosperms.''}

Statistical analysis: the analysis would be more precise if the authors
used Generalized linear mixed models to avoid data transformation and
take into account (with random effects, as they do for the linear mixed
model, LMM, presented now) the influence of species in the analysis.
Then I missed a further discussion on the role of individual species
(e.g.~see my comment below on Rt\textgreater1).

\textbf{A GLMM would only avoid transformation of the dependent variable
(Rt), but that was (and is) not transformed. We tried the analysis with
generalized linear mixed models with a Gaussian distribution, and
confirmed that this gave very similar results, so we are sticking with
LMM.}

I suggest to show some relationship, e.g.~between Rt and traits in
figures. The study only presents two figures and there is plenty of room
to present results more clearly with extra figures.

\textbf{We created a new figure (\emph{Fig. 4}) visualizing the top
model results.}
(\href{https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/71}{\emph{issue
\#71}}()

\textbf{We have \emph{also} added a new figure (\emph{Fig. 2}) showing
how \(Rt\) varied across species in each of the three droughts.}

Only assessing models with AIC is not enough to prove sound
relationships in multidimensional and complex data-models. LL ratio
tests or deviance-anova tests can be used in the case of nested models
with LMM or GLMM respectively. Along the text: dAIC is generally
referred as \(\Delta\)AIC, please change accordingly.

\href{https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/94}{\emph{issue
\#94}}

\textbf{We have gone through the manuscript / tables and figures and
updated where it said ``dAICc'' to be \(\Delta\)AICc. }

@@

Following the two previous comments, I suggest to leave in Table 5 just
the best model (rather that a multimodel inference as is presented now)
to discuss more clearly the covariates included. And I suggest
discussing only the model with all years together. This would be more
robust and avoid ramble differences between years that mostly look
spurious and with a difficult physiological explanation. This would help
to ensure a better use of the Resilience indices.

\textbf{In the spirit of this comment (simplifying presentation), we
have created a new figure (\emph{Fig. 4}) visualizing the results of the
best model. We moved Table 5 to the Appendix (now Table S6, plus a
parallel Table S7 for \(Rt_{ARIMA}\)).}

\textbf{We have also dramatically decreased the emphasis on differences
across drought years, as follows:* }

\textbf{(1) Table 1 now shows just the results from the model with all
drought years combined.}

\textbf{(2) The results and discussion now focus on the results from the
three drought years combined.}

\textbf{(3) In order to make models more consistent across years and
reduce spurious correlations, we now include the criteria that for a
trait to be included as a candidate variable in the full model, the sign
of coefficients must be consistent across all droughts (in addition to
meeting the AIC criteria, as before). This resulted in only two
candidate variables for the main model (\(PLA_{dry}\) and
\(\pi_{tlp}\)). (Removed was ring porosity, which had opposite effects
in different droughts.)}

\emph{We do plot the three droughts separately in figures
\textbf{\#,\#}, as we do fee that this makes the story richer.}

The authors might like to consider including Table 4 as a supplement,
because as it stands it looks like an exploratory analysis. If the
`single-variable approach' is not just exploratory, state it clearly and
why it is needed besides the full models with several parameters.

\textbf{We have moved this table to the SI. We modified the analysis
approach such that separate models for individual variable tests (as
previously show in this table) are now limited to the species traits.
While this table is (and was) the only display item (besides Table 1)
giving these results, the results are either mostly negative (wood
density, SLA, xylem porosity) or preliminary tests qualifying variables
for inclusion in full model (\(PLA_{dry}\) and \(\pi_{tlp}\)).}

Importantly, the drought selection would be biased if years were
selected as from line 202, which is a common mistake in similar studies
(the original of Lloret et al.~included). Droughts must be selected
based only on some climatic/drought index (PDSI, SPEI,\ldots) and
independently of growth. Otherwise the analysis is biased towards years
with low growth, and different questions would arise with a difficult
answer. If the authors select only those droughts where there is a
growth decrease: is that decrease evident in all species and similar
across species? What happens with more intense droughts that those
selected (if any), why they do not force a decrease in growth if drought
is a main forcing agent? I see that 1966 and 1999 are the driest (as in
PDSI) in Figure 1, but there is at least one year around 1955 that it is
as dry or drier than 1977. In line 204 it is stated that they are the
driest. If this is the case, the analysis should be sound but it should
be deleted what is stated in lines 202-203 where authors say that they
selected years also based on low growth. In fact, that should be a
result after having selected the drought years only based on dryness (as
in lines 208-209). Line 211 then they search for pointer years\ldots{} a
little bit messy. Please, explain better, and it should follow: 1)
selection of dry years without regarding growth data; 2) characterise
growth those dry years; 3) If the authors want to compare with other
pointer years, fine, but that should be a third independent step
properly justified and explained. Following this rationale, then in line
221 it should be difficult that Rt\textgreater1, had we selected those
years with a negative growth anomaly. Please, explain clearly and
consistently.

\textbf{We have made the suggested change: we now present only the PDSI
criteria in the methods, and mention the fact that the selected years
were also the ones with largest growth reductions during the study
period in the results section. Using just the PDSI criterion does not
change the years analyzed.}

@@

Other minor comments:

\begin{itemize}
\tightlist
\item
  Line 113: correct `positively'.
\end{itemize}

\textbf{done}

\begin{itemize}
\tightlist
\item
  Line 134: cambial growth also includes that of phloem; so better refer
  to `xylem growth'.
\end{itemize}

\textbf{done}

\begin{itemize}
\tightlist
\item
  Line 161: how many species were estimated for height like this?
  Wouldn't it be possible for authors to go to the field and perform
  some height estimations? This should be rather straightforward and the
  authors would increase accuracy across species in height estimation.
\end{itemize}

\textbf{We have specified how many species used the interspecific
allometry (n=2, JUNI and FRAM). Because of COVID-19, it would not be
possible to go collect more data for these species.}

\begin{itemize}
\tightlist
\item
  Lines 166-167: please explain further the hypothesis and why.
\end{itemize}

\textbf{We have reworded this sentence to read, ``While some tree crowns
undoubtedly changed position over the past several decades, in this case
the bias would be unlikely to result in false acceptance of the
prediction that dominant trees have the lowest \(Rt\) (\emph{i.e.}, type
I error unlikely, type II error possible), making our hypothesis test
conservative.''}

\begin{itemize}
\tightlist
\item
  Line 222: what about climate in years before 1991?
\end{itemize}

\textbf{We no longer mention 1991, as it does not meet the PDSI
criteria.}

\begin{itemize}
\tightlist
\item
  Line 231: define AICc.
\end{itemize}

\textbf{This is done (with added reference)}

\begin{itemize}
\tightlist
\item
  Line 234-247: it is not clear what the authors did, please explain
  clearer this paragraph and the next and why you did two different (yet
  similar) analyses (single-variable and full model).
\end{itemize}

\textbf{This section has been re-written.}

\begin{itemize}
\tightlist
\item
  Line 241-242: enough to say once that models were selected based on
  AIC (line 237-238) and then one criterion, why dAIC\textless1 here and
  dAIC\textless2 before? The classic assumption is 2 (e.g.~Burnham \&
  Anderson 2004). See also my other comment above.
\end{itemize}

\textbf{We have modified this text to read as follows:}

\textbf{``Trait variables were considered appropriate for inclusion in
the main model if they had a consistent direction of response across all
droughts and if their addition to a corresponding null model lacking the
trait improved fit (at \(\Delta\)AICc \(\ge\) 1.0) in at least one
drought year (Table 4). We note that the \(\Delta\)AICc \(\ge\) 1.0
criterion is not a test of significance, but of whether the variable has
enough influence to be considered as a \emph{candidate} variable in full
models.''}

\begin{itemize}
\tightlist
\item
  Line 255-256: but this was already an assumption in M-M (line
  202-203). Please, see my comment below and be consistent along the
  text.
\end{itemize}

\textbf{As stated above, we have removed the \(Rt\) criterion from the
drought identification process, and now present this information for the
first time in this section, adding the following statement: ``Across the
entire study period (1950-2009), the focal drought years were the three
years with the largest fraction of trees exhibiting \(Rt \le 0.7\).''}

\begin{itemize}
\tightlist
\item
  Line 258: so this means that they are no sensitive to the drought?
  Which trees, any species in particular? Is this a consequence of stand
  dynamics shadowing the impact of drought events?
\end{itemize}

\textbf{It's not unprecedented to see some trees exhibit increased
growth during drought, and not surprising. Stand dynamics and other
factors result in a lot of scatter in the relationship between tree
growth and climate, so while the distribution of \(Rt\) in Fig. 1b was
shifted left (normal year should be normally distributed around 1),
there still are some trees with increased growth. Our analysis helps to
work out which trees these were (often shorter trees).}

\textbf{We address this question in the discussion, where we have added
a statement about how this is not unprecedented: ``Across all three
droughts, the majority of trees experienced reduced growth, but a
substantial portion had increased growth (Fig. 1b), potentially due to
decreased leaf area of competitors during the drought, and consistent
with prior observations that smaller trees can exhibit increased growth
rates during drought (Bennett et al.~2015). It is likely because of the
moderate impact of these droughts, along with other factors influencing
tree growth (e.g., stand dynamics), that our best models characterize
only a modest amount of variation''}

\textbf{We have also added a new figure (\emph{Fig. 2}) showing how
\(Rt\) varied across species in each of the three droughts.}

\begin{itemize}
\tightlist
\item
  Line 266-267: why only in 1966? I think this shows that this variable
  is not properly assessed. The older the date, the more accurate the
  estimation of crown position and height were.
\end{itemize}

\textbf{It is true that crown position estimates become more accurate in
later dates, but height should be equally reliable across years, having
been estimated based on reconstructed DBH. This was not previously
clearly specified in the methods. To clarify, we have added the
following statement: ``We then used these allometries to estimate \(H\)
for each drought year, \(Y\), based on reconstructed \(DBH_Y\).''}

\textbf{We agree that the assessment of crown position is somewhat
problematic, both because of its increasing inaccuracy going back
through time, and because of collinearity with \(H\). However, given
that it is both biologically interesting and comes out in our top
models, we have chosen to include it. We note that this makes the test
of our hypothesis conservative. We are transparent about this issue, to
which we devote a paragraph in the discussion (par. 3).}

\emph{see issue on CP!!!!}

\begin{itemize}
\tightlist
\item
  Line 275-280: those profiles were assumed a priori in the introduction
  and are common to any forest. They are indeed interesting to
  characterise the forest, but they do not add to individual tree
  variability. You could think to send Figure 2 to an appendix, in
  consequence, and use figures to show more specific results related to
  your individual tree analyses.
\end{itemize}

### 2020-07-16 manuscript/climate_sensitivity_SI.Rmd
worked on crown position
#112
removed Fig. S3

\newpage
![Figure S3: Height (from reconstructed DBH) by crown position across the three focal droughts and in the year of measurement (2018)](tables_figures/publication/figureS3_height_plot_analysis.png){width=600px}

\newpage
![Figure S4: **PLACEHOLDER** ](tables_figures/publication/independent_variables_by_species.png)

\newpage
![Figure S5: Comparison of $Rt$ and $Rt_{ARIMA}$ results, with residuals, for each drought scenario](tables_figures/publication/figureS4_Rt_arima_comparison.png)

\newpage
![Figure S6: **PLACEHOLDER** ](tables_figures/publication/figureS5_species Rt differences.png)

>>>>

\newpage
![Figure S3: **PLACEHOLDER** ](tables_figures/publication/independent_variables_by_species.png)

\newpage
![Figure S4: Comparison of $Rt$ and $Rt_{ARIMA}$ results, with residuals, for each drought scenario](tables_figures/publication/figureS4_Rt_arima_comparison.png)

\newpage
![Figure S5: **PLACEHOLDER** ](tables_figures/publication/figureS5_species Rt differences.png)

### 2020-07-16 manuscript/climate_sensitivity_draft.Rmd
worked on crown position
#112
removed Fig. S3

Crown position--a categorical variable including dominant, co-dominant, intermediate, and suppressed--was recorded for all cored trees that remained standing during the growing season of 2018 following the protocol of @jennings_assessing_1999. While some tree crowns undoubtedly changed position over the past several decades, in this case the bias would be unlikely to result in false acceptance of the prediction that dominant trees have the lowest $Rt$ (*i.e.*, type I error unlikely, type II error possible), making our hypothesis test conservative. An analysis of crown position relative to height (Fig. **2d**) and height changes since the beginning of the study period indicated that changes between focal drought years (1966, 1977, and 1999; see below) were fairly small relative to differences among crown positions (Fig. **S3**), with average tree height growth confined to ~0.82 m from 1966 to 1977, ~1.45 m from 1977 to 1999, and ~1.97 m from 1999 to 2018. However, dominant and co-dominant trees were similar in height (Figs. **2d**, **S3**).

@@

We then determined the top full models for predicting $Rt$ (or $Rt_{ARIMA}$). 
To do so, we compared models with all possible combinations of candidate variables, including $ln[H]$*$TWI$ or crown position and $TWI$, and species traits as specified above.
Crown position and $ln[H]$ were never considered in the same model because of high correlation (0.73) between the two variables. 
We identified the full set of models within $\Delta$AICc=2 of the best model (that with lowest AICc). 
When a variable appeared in all of these models and the sign of the coefficient was consistent across models, we viewed this as support for the acceptance/rejection of the associated prediction (Table 1). 
If the variable appeared in some but not all of these models, and its sign we was consistent across models, we considered this partial support/rejection. 
In presentation of the results below, we note instances where the $Rt_{ARIMA}$ model disagreed with the $Rt$ model, but otherwise do not discuss the $Rt_{ARIMA}$ model.

>>>>

Crown position--a categorical variable including dominant, co-dominant, intermediate, and suppressed--was recorded for all cored trees that remained standing during the growing season of 2018 following the protocol of @jennings_assessing_1999.

@@

We then determined the top full models for predicting $Rt$ (or $Rt_{ARIMA}$). 
To do so, we compared models with all possible combinations of candidate variables, including $ln[H]$*$TWI$ and species traits as specified above.
We identified the full set of models within $\Delta$AICc=2 of the best model (that with lowest AICc). 
When a variable appeared in all of these models and the sign of the coefficient was consistent across models, we viewed this as support for the acceptance/rejection of the associated prediction (Table 1). 
If the variable appeared in some but not all of these models, and its sign we was consistent across models, we considered this partial support/rejection. 
In presentation of the results below, we note instances where the $Rt_{ARIMA}$ model disagreed with the $Rt$ model, but otherwise do not discuss the $Rt_{ARIMA}$ model.
